CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2023-12-02 paper.Rmd
Fix typos in the paper.

Input data for the PFU database can be found in @Marshall:2023aa.
Access to the full CL-PFU database can be obtained via correspondence 
with author [PEB](mailto:P.E.Brockway@leeds.ac.uk)^[Because the PFU Database contains
primary and final energy [IEA EWEB][link-ieaeweb] data, 
use of the PFU Database
is restricted to those who have access to [IEA][link-iea] [EWEB][link-ieaeweb] data.].
If desired, researchers with access to the 
[IEA][link-iea]'s [EWEB][link-ieaeweb] 
data can create their own CL-PFU database 
following the example below.

>>>>

Input data for the PFU database can be found in @Marshall:2023aa.
Access to the full CL-PFU database can be obtained via correspondence 
with author [PEB](mailto:P.E.Brockway@leeds.ac.uk)^[Because the CL-PFU database contains
primary and final energy [IEA EWEB][link-ieaeweb] data, 
use of the CL-PFU database
is restricted to those who have access to [IEA][link-iea] [EWEB][link-ieaeweb] data.].
If desired, researchers with access to the 
[IEA][link-iea]'s [EWEB][link-ieaeweb] 
data can create their own CL-PFU database 
following the example below.
